Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fixes

%accordingly. If multiple copies make positive predictions, the
%algorithm chooses one of them arbitrarily

@@

\begin{proof}
Let $M = \sum_{t=1}^T z_t$ be the number of
mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
Let $A
= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
number of mistakes in the rounds when $S_t = \emptyset$.
It can be easily seen that $M = A + B$. %We now upper bound $A$ and $B$ separately.

Let $C$ be the number of times line~\ref{line:pos-update} gets executed. Let $U$ be the number of
times line~\ref{line:pos-update} and line~\ref{line:neg-update} get executed. In other words, $U$ is the number of
times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
updated. It can be easily seen that $U = A + C$.

@@

To finish the proof, we need to upper bound the number of updates $U$. We claim
that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2} and
\eqref{equation:strong-linear-separability-3}.
The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
changes only if there is an update in round $t$.
We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
by lines~\ref{line:pos-update} and~\ref{line:neg-update}, we always have
$ w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t $,
and for all $i \neq \widehat y_t$, $w_{i}^{(t+1)} = w_{i}^{(t)}$.
Therefore,
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \norm{w_i^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
\end{align*}
\endgroup
Hence, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
\label{eqn:norm-ub}
\end{equation}
Similarly, if there is an update in round $t$, we have
\begin{align*}
& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
\end{align*}
where the last inequality follows from a case analysis on $z_t$ and
Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2}, we have
that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$;
if $z_t = 1$, then $\widehat y_t \neq y_t$, by Equation~\eqref{equation:strong-linear-separability-3},
we have that $\ip{w_{\widehat y_t}^*}{x_t} \leq -\frac \gamma 2$.

%\eqref{equation:strong-linear-separability-2}
%and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.

Thus, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \frac {\gamma U} 2 \; .
\label{eqn:norm-lb}
\end{equation}
Applying Cauchy-Schwartz's inequality twice, and using assumption
\eqref{equation:strong-linear-separability-1}, we get that
\begin{align*}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
& \le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}} \\
& \le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \\
& \le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
\end{align*}
Combining the above inequality with Equations~\eqref{eqn:norm-ub} and~\eqref{eqn:norm-lb}, we get
$$
(\frac{\gamma U}{2})^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
$$
We conclude that $U \le 4(R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor 4(R/\gamma)^2 \rfloor$.

Applying Equation~\eqref{eqn:mistake-update}, we get
\[ \Exp[M] \leq (K-1) \Exp[U] \leq (K-1) \lfloor 4(R/\gamma)^2 \rfloor. \qedhere \]
\end{proof}

@@

Define a filtration $\cbr{\calB_j}_{j=0}^M$,
where $\calB_j = \sigma((x_1, y_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}))$
for every $j$ in $\{1,2,\dots,M\}$.
By Claim 2 of~\cite{Daniely-Helbertal-2013}, as $\ell_j$
is chosen uniformly from $\cbr{1,\ldots,K}$ and independent of $\calB_{j-1}$,
\[ \Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t \Bigg| \calB_{j-1} } \geq \frac{K-1}2. \]
This implies that
\[ \Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \geq \frac{K-1}2. \]
Summing over all $j$ in $\{1,2,\dots,M\}$,
\[ \Exp \sbr{ \sum_{t=1}^{(K-1)M} z_t} \geq \frac{K-1}2 \cdot M = \frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor. \]

@@

\begin{algorithm}[h]
\caption{\textsc{Kernelized Bandit Algorithm}
\label{algorithm:kernelized}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$.}
\REQUIRE{Number of rounds $T$.}
\REQUIRE{Kernel function  $k(\cdot, \cdot)$.}
\STATE{Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$.}
\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

>>>>

@@

\begin{proof}
Let $M = \sum_{t=1}^T z_t$ be the number of
mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
Let $A
= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
number of mistakes in the rounds when $S_t = \emptyset$.
It can be easily seen that $M = A + B$.

Let $C$ be the number of times line~\ref{line:pos-update} gets executed. Let $U$
be the number of times line~\ref{line:pos-update} or line~\ref{line:neg-update}
get executed. In other words, $U$ is the number of times the $K$-tuple of
vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
easily seen that $U = A + C$.

@@

To finish the proof, we need to upper bound the number of updates $U$. We claim
that $U \le \lfloor 4(R/\gamma)^2 \rfloor$. The proof of this upper bound is
similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2} and
\eqref{equation:strong-linear-separability-3}.
The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
changes only if there is an update in round $t$.
We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
by lines~\ref{line:pos-update} and~\ref{line:neg-update}, we always have
$ w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t $,
and for all $i \neq \widehat y_t$, $w_{i}^{(t+1)} = w_{i}^{(t)}$.
Therefore,
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \norm{w_i^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
\end{align*}
\endgroup
Hence, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
\label{eqn:norm-ub}
\end{equation}
Similarly, if there is an update in round $t$, we have
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
\end{align*}
\endgroup
where the last inequality follows from a case analysis on $z_t$ and
Definition~\ref{definition:strong-linear-separability}: if $z_t = 0$, then
$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
then $\widehat y_t \neq y_t$, by
Equation~\eqref{equation:strong-linear-separability-3}, we have that
$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.

Thus, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \frac {\gamma U} 2 \; .
\label{eqn:norm-lb}
\end{equation}
Applying Cauchy-Schwartz's inequality twice, and using assumption
\eqref{equation:strong-linear-separability-1}, we get that
\begin{align*}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
& \le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}} \\
& \le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \\
& \le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
\end{align*}
Combining the above inequality with Equations~\eqref{eqn:norm-ub} and~\eqref{eqn:norm-lb}, we get
$$
\left(\frac{\gamma U}{2} \right)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
$$
We conclude that $U \le 4(R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor 4(R/\gamma)^2 \rfloor$.

Applying Equation~\eqref{eqn:mistake-update}, we get
$$
\Exp[M] \leq (K-1) \Exp[U] \leq (K-1) \lfloor 4(R/\gamma)^2 \rfloor \; . \qedhere
$$
\end{proof}

@@

Define a filtration $\cbr{\calB_j}_{j=0}^M$,
where $\calB_j = \sigma((x_1, y_1), \ldots, (x_{(K-1)j}, y_{(K-1)j}))$
for every $j$ in $\{1,2,\dots,M\}$.
By Claim 2 of~\citet{Daniely-Helbertal-2013}, as $\ell_j$
is chosen uniformly from $\cbr{1,\dots,K}$ and independent of $\calB_{j-1}$,
$$
\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t ~\Bigg|~ \calB_{j-1} } \geq \frac{K-1}2 \; .
$$
This implies that
$$
\Exp \sbr{ \sum_{t=(K-1)(j-1) + 1}^{(K-1)j} z_t } \ge \frac{K-1}2 \; .
$$
Summing over all $j$ in $\{1,2,\dots,M\}$,
$$
\Exp \sbr{ \sum_{t=1}^{(K-1)M} z_t} \geq \frac{K-1}2 \cdot M = \frac{K-1}2 \left\lfloor \frac 1 4 (R/\gamma)^2 \right\rfloor \; .
$$

@@

\begin{algorithm}[h]
\caption{\textsc{Kernelized Bandit Algorithm}
\label{algorithm:kernelized}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$.}
\REQUIRE{Number of rounds $T$.}
\REQUIRE{Kernel function  $k(\cdot, \cdot)$.}
\STATE{Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$.}
\STATE{Compute \\ $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

### 2019-01-14 ICML-submission/notions-of-linear-separability.tex
Fixes

The notion of strong linear separability has appeared in the literature;
see e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
Conservative OVA algorithm with PA-I update has a finite mistake bound under the strong
linear separability assumption, their proof of Theorem 2 is incorrect. Their
Lemma 4 cannot be directly applied to the bandit setting,
as the algorithm only makes updates on a subset of the $w_i$'s.}
Intuitively, strong linear
separability means that, for each class $i$, the set of examples belonging to class $i$ and
the set of example belonging to the remaining $K-1$ classes are separated by
a linear classifier $w_i$ by a margin $\frac \gamma 2$.
%Formally, $w_i$ separates the set of examples $\cbr{(x_t, y_t): t \in
%\cbr{1,\ldots,T}, y_t = i}$ and $\cbr{(x_t, y_t): t \in \cbr{1,\ldots,T}, y_t
%\neq i}$.

%\chicheng{I think the notion has appeared in, however,
%they proposed an algorithm that doesn't achieve a finite mistake bound in the bandit
%setting under this assumption (although they claimed that they have done so, the proof was
%wrong..)}

@@

%with margin $\gamma' = 2\gamma$.

In the special case of $K=2$, if a set of labeled examples are weakly linearly separable with a margin
$\gamma$, then they are strongly linearly separable with the same margin.
Indeed, if $w_1, w_2$ satisfy \eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$, $w_2' =
\frac{w_2 - w_1}{2}$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}.
The first condition follows from $\norm{w_i'}^2 \le (\frac{1}{2}
\norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le \frac{1}{2}\norm{w_1}^2 +
\frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$. The last two condition
follows from the fact that $w_1' - w_2' = w_1 - w_2$.
However, for any $K \ge 3$ and any inner product space of dimension at least
$2$, there exists a set of labeled examples that is weakly linearly separable with a
positive margin $\gamma$ but it is not strongly linearly separable with any
positive margin $\gamma$. An example of such set of labeled examples is shown in
Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}.

%\chicheng{Shall we change the $\gamma$ in Equations
%\eqref{equation:strong-linear-separability-2},
%\eqref{equation:strong-linear-separability-3} to $\gamma/2$, to simplify the
%presentation?}

>>>>

The notion of strong linear separability has appeared in the literature; see
e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
Conservative OVA algorithm with PA-I update has a finite mistake bound under the
strong linear separability assumption, their proof of Theorem 2 is incorrect.
Their Lemma 4 cannot be directly applied to the bandit setting, as the algorithm
only makes updates on a subset of the $w_i$'s.} Intuitively, strong linear
separability means that, for each class $i$, the set of examples belonging to
class $i$ and the set of example belonging to the remaining $K-1$ classes are
separated by a linear classifier $w_i$ by a margin $\frac \gamma 2$.

@@

In the special case of $K=2$, if a set of labeled examples are weakly linearly
separable with a margin $\gamma$, then they are strongly linearly separable with
the same margin. Indeed, if $w_1, w_2$ satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
$w_2' = \frac{w_2 - w_1}{2}$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}. The first condition follows from
$\norm{w_i'}^2 \le (\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le
\frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
The last two condition follows from the fact that $w_1' - w_2' = w_1 - w_2$.

However, for any $K \ge 3$ and any inner product space of dimension at least
$2$, there exists a set of labeled examples that is weakly linearly separable
with a positive margin $\gamma$ but it is not strongly linearly separable with
any positive margin $\gamma$. An example of such set of labeled examples is
shown in~\autoref{figure:weakly-linearly-separable-examples-with-margin}.

### 2019-01-14 ICML-submission/related-work.tex
Fixes

The problem of online bandit multiclass learning was initially formulated
in the pioneering work of~\cite{Auer-Long-1999}, under the name of
``weak reinforcement model''. They show that if the set of examples shown is
separable by a classifier in a prespecified hypothesis class $\calH$, then the optimal
 mistake bound in the bandit setting can be upper bounded by the optimal mistake
 bound in the full-information setting, times a factor of $(2.01 + o(1))K \ln K$.
 (See~\cite{Long-2017} for improvements of the factor to $(1 + o(1)) K \ln K$.)
 ~\cite{Daniely-Helbertal-2013} extend the results to the setting where the
 performance of the algorithm is measured by its regret, i.e. the difference
 between the number of mistake made by the algorithm and the number of mistake
 made by the best classifier in $\calH$ in hindsight. However, all algorithms developed in
 this context are computationally inefficient.

>>>>

The problem of online bandit multiclass learning was initially formulated in the
pioneering work of~\citet{Auer-Long-1999} under the name of ``weak reinforcement
model''. They show that if the set of examples shown is separable by a
classifier in a prespecified hypothesis class $\calH$, then the optimal mistake
bound in the bandit setting can be upper bounded by the optimal mistake bound in
the full-information setting, times a factor of $(2.01 + o(1))K \ln K$.
\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$.
\citet{Daniely-Helbertal-2013} extend the results to the setting where the
performance of the algorithm is measured by its regret, i.e. the difference
between the number of mistake made by the algorithm and the number of mistake
made by the best classifier in $\calH$ in hindsight. However, all algorithms
developed in this context are computationally inefficient.
